Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-05-17 WSSSPE4_report/WSSSPE4_paper.tex
fixing typo
another error

The participants were given time after the presentation to write down their comments.
Seven people volunteered to work on revising the mission and vision statements, incorporating these comments and presenting back to the community.
Based on this feedback, the committee redrafted the mission and vision.
The committee added focus areas to clarify the organizations breadth and to keep the mission and vision simple and long-lasting.
Comments after the close of the meeting were incorporated into the statements.

@@

WSSSPE included the presentation of 12 10-minute talks (based on four idea papers, three position papers,
two experience papers, and three demos) that addressed a wide range of topics around
sustainability for software in science. These talks covered three main areas.

>>>>

The participants were given time after the presentation to write down their comments.
Seven people volunteered to work on revising the mission and vision statements, incorporating these comments and presenting back to the community.
Based on this feedback, the committee redrafted the mission and vision.
The committee added focus areas to clarify the organization's breadth and to keep the mission and vision simple and long-lasting.
Comments after the close of the meeting were incorporated into the statements.

@@

WSSSPE4 included the presentation of 12 10-minute talks (based on four idea papers, three position papers,
two experience papers, and three demos) that addressed a wide range of topics around
sustainability for software in science. These talks covered three main areas.

### 2017-05-17 WSSSPE4_report/WSSSPE4_report.tex
fixing typo
another error

WSSSPE included the presentation of 12 10-minute talks (based on four idea papers, three position papers,
two experience papers, and three demos) that addressed a wide range of topics around
sustainability for software in science. These talks covered three main areas:
\begin{enumerate}
\item The specifics of the academic environment for software development and for so-called
research programmers or research software engineers;
\item The characteristics and needs of research software in general such as the lifecycle of
software in science, preservation, curation, sharing, and reproducibility challenges; and
\item Lessons learned from or visions for use cases of scientific software and communities
working with and\slash or on a software package.
\end{enumerate}

>>>>

WSSSPE4 included the presentation of 12 10-minute talks (based on four idea papers, three position papers,
two experience papers, and three demos) that addressed a wide range of topics around
sustainability for software in science. These talks covered three main areas:
\begin{enumerate}
\item The specifics of the academic environment for software development and for so-called
research programmers or research software engineers;
\item The characteristics and needs of research software in general such as the lifecycle of
software in science, preservation, curation, sharing, and reproducibility challenges; and
\item Lessons learned from or visions for use cases of scientific software and communities
working with and\slash or on a software package.
\end{enumerate}
